---
title: "Machine Learning Course Project"
author: "Teng FENG"
date: "January 31, 2016"
output: html_document
---

### Executive Summary
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. The goal of the project is to predict the manner in which they did the exercise. 

### Load the data
```{r}
rm(list = ls())
download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", destfile = "pml-training.csv")
download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", destfile = "pml-testing.csv")
training <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")
```

### Cleaning the data
Remove the first 7 columns which are not necessary for the analysis and all the columns containing NA or "".
```{r}
training <- subset(training, select = -c(1:7))
training <- training[, apply(training, 2, function(x)!any(is.na(x) | x == ""))]
```

### Modeling the data

Fisrt we need to create data partition.
```{r}
library(caret)
set.seed(12345)
inTrain <- createDataPartition(y = training$classe, p = .7, list = F)
training1 <- training[inTrain,]
testing1 <- training[-inTrain,]
```

Now we apply the Random Forest with 5 fold cross validation.
```{r}
Mod <- train(classe ~., method = "rf", data = training1, trControl = trainControl(method = ("cv"), number = 5))
```

Testing the model on testing1
```{r}
pred <- predict(Mod, newdata = testing1)
confusionMatrix(pred, testing1$classe)
```

The accuracy is 98.95% and the OOS Error Rate is 1.05%.

### Testing the model on "testing"
```{r}
pred1 <- predict(Mod, newdata = testing)
pred1
```
